### 2013-10-01 Publications/2013-ISBI14/03-methods.tex
Andres' comments

To evaluate the influence of
distortions on the final connectivity outcome,
an intermediate step was also implemented to
produce deterministic tractography,
using the \emph{Diffusion Toolkit} \cite{wang_diffusion_2007}.
The original phantom, one distorted version, and
the corrected instances are fed to this module.
Additionally, the original tissue probability maps
are also distorted and corrected, for computing overlap
indices.
Each tractography was restricted to its corresponding 
\gls*{wm} mask, after distortion and correction when
applied. For all the cases, we used 10 random seeds at each seeding
voxel and the seeding voxels were taken from the 
ground-truth, mimicking the usual procedure on real data
(where regions are typically mapped from the
anatomically correct T1).

The evaluation framework is completed by automated 
assessment modules. We evaluated three characteristics
of the correction methods. 
Firstly, we assessed the geometrical correctness
reporting overlap indices of three tissue
probability maps (namely \gls*{csf}, \gls*{wm},
and \gls*{gm}), weighting the average by tissue
volumes.
Secondly, to evaluate the quality of the actual 
signal dropout correction, we studied the 
similarity volume by volume computing the $\ell_1$-norm
correlation index. We report this score
on the \textit{b0} and the average of the remaining 32 
\glspl*{dwi}. Thirdly, we studied the impact on the
connectivity matrices reporting the number of
false positives (inexistent connections in the
gold-standard) and false negatives (or connections
lost).

>>>>

To evaluate the influence of
distortions on the final connectivity outcome,
an intermediate step was also implemented to
produce deterministic tractography,
using the \emph{Diffusion Toolkit} \cite{wang_diffusion_2007}.
The original phantom, one distorted version, and
the corrected instances are fed to this module.
Additionally, the original tissue probability maps
are also distorted and corrected, for computing overlap
indices.
Each tractography was restricted to its corresponding 
\gls*{wm} mask, after distortion and correction when
applied. For all the cases, we used 10 random seeds at each seeding
voxel (belonging to one out of 27 different seeding regions).
The seeding regions were taken from the 
ground-truth, mimicking the usual procedure on real data
(where regions are typically mapped from the
anatomically correct T1).

The evaluation framework is completed by automated 
assessment modules. We evaluated three characteristics
of the correction methods. 
Firstly, we assessed the geometrical correctness
reporting overlap indices of three tissue
probability maps (namely \gls*{csf}, \gls*{wm},
and \gls*{gm}), weighting the average by tissue
volumes.
Secondly, to evaluate the quality of the actual 
signal dropout correction, we studied the 
similarity volume by volume computing the $\ell_1$-norm
correlation index. We report this score
on the \textit{b0} and the average of the remaining 32 
volumes. Thirdly, we studied the impact on the
connectivity matrices reporting the number of
false positives (inexistent connections in the
gold-standard) and false negatives (or connections
lost).
